A Large-scale Study of Polymorphism in R

### 2019-04-05 paper/main.tex
discussed a table in results

Here, we've made a number of small discoveries.
We see environments, which are essentially dignified lists (i.e., they are lists with a parent list, and are used to implement scoping).
\AT{Possibly explain some of these? Dunno.}

>>>>

Table~\ref{tab:L2top10argwclass} does indeed showcase some interesting classes.
The three builtin classes which we have not yet seen are environment, formula, and array.
An environments is a list which has a references to a parent environment (another list with environment class).
A formula is a \AT{small explanation}.
An array is a generalization of a matrix in R, where an array can have more than 2 dimensions.
Each of the other classes pictured here are defined in some package, and are not part of the base language.
An interesting fact about this table is that all of the pictures signatures are monomorphic.

%Here, we've made a number of small discoveries.
%We see environments, which are essentially dignified lists (i.e., they are lists with a parent list, and are used to implement scoping).
%\AT{Possibly explain some of these? Dunno.}
